\thetitle

### 2022-03-22 paper/paper.tex
improved plot quality, type assertions

\begin{example} \label{tightexampleforoneoverhopt}
\ifen
Pick any $h$ and let $m = 2h$. For a small constant $\varepsilon \in (0, 1)$, construct the market as follows.
\else
임의의 $h$를 택하고 $m = 2h$라고 하자. 작은 상수  $\varepsilon \in (0, 1)$에 대해 시장을 다음처럼 구성한다.
\fi
\begin{align*}
t &= \Bigl(\,\underbrace{1,  \dots, 1}_{h},\;
\underbrace{\varepsilon^{-1}, \varepsilon^{-2}, \dots, \varepsilon^{-(h-1)}, \varepsilon^{-h}}_{h}\,\Bigr) \\
\text{and}\quad f &= \Bigl(\,\underbrace{1,  \dots, 1}_{h},\;
\underbrace{\varepsilon^{1}, \varepsilon^{2}, \dots, \varepsilon^{h-1}, \varepsilon^{h}}_{h}\,\Bigr)
\end{align*}
\ifen
Since all $f_j t_j = 1$, the na\"ive algorithm can choose $\mathcal{T}_h = \{1, \dots, h\}$, with $v(\mathcal{T}_h) = 1$. But the optimal solution is $\mathcal{X}_h = \{h+1, \dots, m\}$, with
\else
모든 $f_j t_j = 1$이므로 나이브 해법은 $\mathcal{T}_h = \{1, \dots, h\}$를 출력할 수 있으며 $v(\mathcal{T}_h) = 1$이다. 그러나 최적해는 $\mathcal{X}_h = \{h+1, \dots, m\}$이며 그의 기대 효용은 다음과 같다.
\fi
\begin{equation*}
v(\mathcal{X}_h) = \sum_{j= h +1}^m \Bigl( f_j t_j \prod_{j' = j+1}^m (1 - f_{j'}) \Bigr) =  \sum_{j= 1}^h  (1 - \varepsilon)^{j} \approx h\ifen.\fi
\end{equation*}
\ifen
Thus, as $\varepsilon$ approaches zero, we have $v(\mathcal{T}_h) / v(\mathcal{X}_h) \to 1/h$. (The optimality of $\mathcal{X}_h$ follows from the fact that it achieves the upper bound of Theorem \ref{oneoverhopt}.)
\else
따라서 $\varepsilon$이 0에 가까워지면서 $v(\mathcal{T}_h) / v(\mathcal{X}_h) \to 1/h$이 된다.  ($\mathcal{X}_h$의 최적성은 정리 \ref{oneoverhopt}이(가) 제시하는 상한을 실천하기 때문에 성립한다.)
\fi
\end{example}

@@

\ifen
Below are shown the first several iterations of Algorithm \ref{algorithmforlargeh}. The values of $f_j$, $t_j$, and their product are recorded only for the schools remaining in $\mathcal{C}$. $f * t$, where $(f * t)_j = f_j t_j$, denotes the entrywise product of $f$ and $t$. The school added at each iteration, underlined, is the one whose $f_j t_j$-value is greatest.
\else
아래에서 알고리즘 \ref{algorithmforlargeh}의 몇 반복단계가 나타난다. $f_j$, $t_j$, 그리고 그 곱의 값은 $\mathcal{C}$에 남아 있는 학교에 해당하는 값만 기록한다. $(f * t)_j = f_j t_j$로 정의된 $f * t$는 $f$와 $t$의 원소 당 곱을 의미한다. 각 반복단계에서 최적해에 추가하는 학교는 $f_j t_j$-값이 가장 높은 학교이며 이를 밑줄로 강조한다.
\fi
\newcommand{\Iteration}{\ifen Iteration~\else 반복단계~\fi}
\begin{align*}
\text{\Iteration 1:}
&&C &= \{1, 2, 3, 4, 5, 6, 7, 8\} \\
&&f &= \{0.39, 0.33, 0.24, 0.24, 0.05, 0.03, 0.1, 0.12\} \\
&&t &= \{200, 250, 300, 350, 400, 450, 500, 550\} \\
&&f * t &= \{78.0, 82.5, 72.0, \underline{84.0}, 20.0, 13.5, 50.0, 66.0\} 
~~\tag*{\(\implies \mathcal{X}_3 = \{4\} \)}\\
\text{\Iteration 2:}
&&C &= \{1, 2, 3, 5, 6, 7, 8\} \\
&&f &= \{0.39, 0.33, 0.24, 0.05, 0.03, 0.1, 0.12\} \\
&&t &= \{152, 190, 228, 316, 366, 416, 466\} \\
&&f * t &= \{59.28, \underline{62.7}, 54.72, 15.8, 10.98, 41.6, 55.92\} 
~~\tag*{\(\implies \mathcal{X}_3 = \{4, 2\} \)}\\
\text{\Iteration 3:}
&&C &= \{1, 3, 5, 6, 7, 8\} \\
&&f &= \{0.39, 0.24, 0.05, 0.03, 0.1, 0.12\} \\
&&t &= \{101.84, 165.3, 253.3, 303.3, 353.3, 403.3\} \\
&&f * t &= \{39.718, 39.672, 12.665, 9.099, 35.33, \underline{48.396}\} 
~~\tag*{\(\implies \mathcal{X}_3 = \{4, 2, 8\} \)}\\
&&&\cdots\\
\text{\Iteration 8:}
&&C &= \{6\}, f = \{0.03\}, t = \{177.622\}, f * t= \{\underline{5.329}\}
~~\tag*{\(\implies \mathcal{X}_3 = \{4, 2, 8, 1, 7, 3, 5, 6\} \)}
\end{align*}
\ifen 
The output of the algorithm is $\mathtt{X} = [4, 2, 8, 1, 7, 3, 5, 6]$, and the optimal $h$-portfolio consists of its first $h$ entries. The ``priority'' column of Table \ref{planetsdata} shows the inverse permutation of $\mathtt{X}$, which is the minimum value of $h$ for which the school is included in the optimal portfolio. Figure \ref{planetsplot} shows the value of the optimal portfolio as a function of $h$. The concave shape of the plot suggests the result of Theorem \ref{concavityinh}. 
\else
알고리즘의 출력은 $\mathtt{X} = [4, 2, 8, 1, 7, 3, 5, 6]$이며 최적 $h$-포트폴리오는 그의 첫 $h$개의 원소로 이루어진다. 표 \ref{planetsdata}에서 등장하는 ``지원 순위'' 자료는 $\mathtt{X}$의 역순열(inverse permutation)이며 이는 해당 학교가 최적 포트폴리오에 포함되는 최소 $h$-값을 의미한다. 그림 \ref{planetsplot}은 최적 포트폴리오의 가치를 $h$의 함수로 나타낸다. 곡선의 오목성은 정리 \ref{concavityinh}의 결과를 시사한다.
\fi

\begin{table}[h!] \centering
\begin{tabular}{r|lcccc}
\ifen\textbf{Index $j$} & \textbf{School $c_j$} & \textbf{Utility $t_j$} & \textbf{Admit prob. $f_j$} & \textbf{Priority} & \textbf{$v(\mathcal{X}_h)$} \\ \hline
\else 
\textbf{지표 $j$} & \textbf{학교 $c_j$} & \textbf{효용 $t_j$} & \textbf{합격 확률 $f_j$} & \textbf{지원 순위} & \textbf{$v(\mathcal{X}_h)$} \\ \hline  \fi
\\[-.75em]
1 & \ifen Mercury University   \else  수성대       \fi        & 200 & 0.39 & 4   & 230.0   \\
2 & \ifen Venus University     \else  금성대       \fi        & 250 & 0.33 & 2   & 146.7  \\
3 & \ifen Mars University      \else  화성대       \fi        & 300 & 0.24 & 6   & 281.5  \\
4 & \ifen Jupiter University   \else  목성대       \fi        & 350 & 0.24 & 1   & \phantom{0}84.0  \\
5 & \ifen Saturn University    \else  토성대       \fi        & 400 & 0.05 & 7   & 288.8  \\
6 & \ifen Uranus University    \else  천왕성대     \fi        & 450 & 0.03 & 8   & 294.1  \\
7 & \ifen Neptune University   \else  해왕성대     \fi        & 500 & 0.10 & 5   & 257.7  \\
8 & \ifen Pluto College        \else  명왕성대       \fi        & 550 & 0.12 & 3   & 195.1              
\end{tabular}
\caption{\label{planetsdata}
\ifen College data and optimal application portfolios for a fictional market with $m=8$ schools. By the nestedness property (Theorem \ref{nestedapplication}), the optimal portfolio when the application limit is $h$ consists of the $h$ schools having priority number $h$ or less.
\else
$m=8$개의 학교로 이루어진 가상 입학 시장의 대학교 자료와 최적 지원 포트폴리오. 포함 사슬 관계 성질(정리 \ref{nestedapplication})에 따라, 지원 제한이 $h$일 때 최적 포트폴리오는 지원 순위가 $h$ 이하인 $h$개의 학교로 구성된다.
\fi}
\end{table}

@@

\ifen \subsection{Summary of results} \else \subsection{결과 정리}\fi
\ifen
In our first experiment, we compare the performance of Algorithm \ref{algorithmforlargeh} for homogeneous-cost markets of various sizes when the set of candidate schools $\mathcal{C}$ is stored as a list and as a binary max heap ordered by the $f_j \bar t_j$-values. The results appear in Table \ref{experiment1results}. Our results indicate that the list implementation is faster. However, the ratio between the average times of the two implementations stays roughly constant at about 1.5, suggesting that a more effective heap implementation could be competitive in certain classes of problem instances. Overall, the rate of growth is quadratic in $m$, which accords with the $O(hm)$ time complexity result of Theorem \ref{validityofalmaalgorithm}.
\else
첫번째 실험에서, 동일한 지원 비용으로 정의된 크기가 다양한 시장에 대해 알고리즘 \ref{algorithmforlargeh}의 성능을 고려했다. 이를 $\mathcal{C}$를 목록 혹은 $f_j \bar t_j$-값에 따라 배열된 힙 구현으로 구성하는 경우로 나눴으며 실험 결과는 표 \ref{experiment1results}에서 등장한다. 실험 결과에 따라 목록 구현이 더 빠른 해법이었다. 그러나, 두개의 방법 사이에 계산 시간 비율은 1.5같은 상수에 가까우므로 개선된 힙 해법이 어떤 문제 인스턴스에 대해 더 빠를 가능성이 있어 보인다. 전체적으로 계산 시간은 $m$의 제곱으로 늘아나며 이는 정리 \ref{validityofalmaalgorithm}에서 말한 $O(hm)$-시간과 동의한다.
\fi

@@

\begin{table}[h!] \centering
\begin{tabular}{r|r@{~}r|r@{~}r}
\ifen 
 \textbf{\begin{tabular}[r]{@{}r@{}}Number of\\schools $m$\end{tabular}}& \multicolumn{2}{c|}{\textbf{\begin{tabular}[c]{@{}c@{}}Algorithm \ref{algorithmforlargeh}\\with list\end{tabular}}}  & \multicolumn{2}{c}{\textbf{\begin{tabular}[c]{@{}c@{}}Algorithm \ref{algorithmforlargeh}\\with heap\end{tabular}}}\\ \hline
 \else
 \textbf{\begin{tabular}[r]{@{}r@{}}학교의\\개수 $m$\end{tabular}}& \multicolumn{2}{c|}{\textbf{\begin{tabular}[c]{@{}c@{}}알고리즘 \ref{algorithmforlargeh}\\(목록 구현)\end{tabular}}}  & \multicolumn{2}{c}{\textbf{\begin{tabular}[c]{@{}c@{}}알고리즘 \ref{algorithmforlargeh}\\(힙 구현)\end{tabular}}}\\ \hline
 \fi
    16 &       0.07 &    (0.02) &      0.06 &    (0.02) \\
    64 &       0.72 &    (0.21) &      0.73 &    (0.21) \\
   256 &      10.36 &    (2.88) &     10.74 &    (3.34) \\
  1024 &     182.14 &   (47.83) &    181.95 &   (29.10) \\
  4096 &    2858.49 &  (123.99) &   2994.55 &  (213.49)            
\end{tabular}
\caption{\label{experiment1results}
\ifen Time to compute an optimal portfolio for an admissions market with homogeneous application costs using Algorithm \ref{algorithmforlargeh} when $\mathcal{C}$ is stored as a list and as a heap. \lastptofcaption~In every case, $h = m/2$. 
\else 알고리즘 \ref{algorithmforlargeh}에서 $\mathcal{C}$를 목록 또는 힙 구현으로 저장했을 때, 
동일 지원 비용 입학 시장의 최적 지원 포트폴리오를 계산하는 시간. \lastptofcaption~모든 경우, $h = m/2$. \fi}
\end{table}

\begin{table}[h!] \centering
\begin{tabular}{r|r@{~}r|r@{~}r|r@{~}r|r@{~}r}
\ifen
\textbf{\begin{tabular}[r]{@{}r@{}}Number of\\schools $m$\end{tabular}}&\multicolumn{2}{c|}{\textbf{\begin{tabular}[c]{@{}c@{}}Algorithm \ref{ellisbnb}:\\Branch \& bound\end{tabular}}}  & \multicolumn{2}{c|}{\textbf{\begin{tabular}[c]{@{}c@{}}Algorithm \ref{ellisDP1}:\\App. costs DP\end{tabular}}}  &\multicolumn{2}{c|}{\textbf{\begin{tabular}[c]{@{}c@{}}Algorithm \ref{ellisDP3}:\\FPTAS, $\varepsilon= 0.5$\end{tabular}}}  & \multicolumn{2}{c}{\textbf{\begin{tabular}[c]{@{}c@{}}Algorithm \ref{ellisDP3}:\\FPTAS, $\varepsilon= 0.05$\end{tabular}}}   \\ \hline
\else
\textbf{\begin{tabular}[r]{@{}r@{}}학교의\\개수 $m$\end{tabular}}&\multicolumn{2}{c|}{\textbf{\begin{tabular}[c]{@{}c@{}}알고리즘  \ref{ellisbnb}:\\분지한계법\end{tabular}}}  & \multicolumn{2}{c|}{\textbf{\begin{tabular}[c]{@{}c@{}}알고리즘 \ref{ellisDP1}: 지원\\비용 동적 계획\end{tabular}}}  &\multicolumn{2}{c|}{\textbf{\begin{tabular}[c]{@{}c@{}}알고리즘 \ref{ellisDP3}:\\FPTAS, $\varepsilon= 0.5$\end{tabular}}}  & \multicolumn{2}{c}{\textbf{\begin{tabular}[c]{@{}c@{}}알고리즘 \ref{ellisDP3}:\\FPTAS, $\varepsilon= 0.05$\end{tabular}}}   \\ \hline
\fi
   8 &          0.44 &       (0.42) &         0.06 &      (0.02) &                0.39 &             (0.16) &                 1.66 &              (0.64) \\
  16 &       3298.08 &    (5285.45) &         0.48 &      (0.16) &                2.64 &             (0.96) &                19.20 &              (7.05) \\
  32 &             — &          (—) &         2.30 &      (0.83) &               19.01 &             (9.18) &               184.00 &             (70.15) \\
  64 &             — &          (—) &         8.33 &      (3.52) &              101.05 &            (59.47) &              2089.30 &            (961.43) \\
 128 &             — &          (—) &        36.61 &     (15.36) &              481.61 &           (210.68) &              8626.29 &           (2615.38) \\
 256 &             — &          (—) &       205.57 &     (52.98) &             3106.71 &           (957.95) &             69291.93 &          (34881.04) \\
 512 &             — &          (—) &      1136.18 &    (396.24) &            16613.99 &          (6241.99) &            206020.31 &          (45217.42) 
\end{tabular}%
\caption{\label{experiment2results}
\ifen Time to compute an optimal or $(1 - \varepsilon)$-optimal portfolio for an admissions market with heterogeneous application costs using the three algorithms developed in section \ref{hetappcosts}.
%branch-and-bound routine (Algorithm \ref{ellisbnb}), exact dynamic program (Algorithm \ref{ellisDP1}), and the fully polynomial-time approximation scheme (Algorithm \ref{ellisDP3}).
The branch-and-bound algorithm is impractical for large markets. \lastptofcaption
\else  %분지한계법 (알고리즘 \ref{ellisbnb}), 정확한 동적 계획 (알고리즘 \ref{ellisDP1}), 그리고 완전 다항 시간 근사 해법 (알고리즘 \ref{ellisDP3})을
 \ref{hetappcosts}절에서 도출한 3개의 알고리즘을 사용할 때, 다양한 지원 비용으로 갖춘 입학 시장의 최적 또는 $(1- \varepsilon)$-최적 포트폴리오를 계산하는 시간. 분지한계법은 큰 시장에서 비실용적이다. \lastptofcaption \fi}
\end{table}

@@

>>>>

\begin{example} \label{tightexampleforoneoverhopt}
\ifen
Pick any $h$ and let $m = 2h$. For a small constant $\varepsilon \in (0, 1)$, define the market as follows.
\else
임의의 $h$를 택하고 $m = 2h$라고 하자. 작은 상수  $\varepsilon \in (0, 1)$에 대해 시장을 다음처럼 구성한다.
\fi
\begin{align*}
t &= \Bigl(\,\underbrace{1,  \dots, 1}_{h},\;
\underbrace{\varepsilon^{-1}, \varepsilon^{-2}, \dots, \varepsilon^{-(h-1)}, \varepsilon^{-h}}_{h}\,\Bigr) \\
\text{and}\quad f &= \Bigl(\,\underbrace{1,  \dots, 1}_{h},\;
\underbrace{\varepsilon^{1}, \varepsilon^{2}, \dots, \varepsilon^{h-1}, \varepsilon^{h}}_{h}\,\Bigr)
\end{align*}
\ifen
Since all $f_j t_j = 1$, the na\"ive algorithm can choose $\mathcal{T}_h = \{1, \dots, h\}$, with $v(\mathcal{T}_h) = 1$. But the optimal solution is $\mathcal{X}_h = \{h+1, \dots, m\}$, with
\else
모든 $f_j t_j = 1$이므로 나이브 해법은 $\mathcal{T}_h = \{1, \dots, h\}$를 출력할 수 있으며 $v(\mathcal{T}_h) = 1$이다. 그러나 최적해는 $\mathcal{X}_h = \{h+1, \dots, m\}$이며 그의 기대 효용은 다음과 같다.
\fi
\begin{equation*}
v(\mathcal{X}_h) = \sum_{j= h +1}^m \Bigl( f_j t_j \prod_{j' = j+1}^m (1 - f_{j'}) \Bigr) =  \sum_{j= 1}^h  (1 - \varepsilon)^{j} \approx h\ifen.\fi
\end{equation*}
\ifen
Thus, as $\varepsilon$ approaches zero, we have $v(\mathcal{T}_h) / v(\mathcal{X}_h) \to 1/h$. (The optimality of $\mathcal{X}_h$ follows from the fact that it achieves the upper bound of Theorem \ref{oneoverhopt}.)
\else
따라서 $\varepsilon$이 0에 가까워지면서 $v(\mathcal{T}_h) / v(\mathcal{X}_h) \to 1/h$이 된다.  ($\mathcal{X}_h$의 최적성은 정리 \ref{oneoverhopt}이(가) 제시하는 상한을 실천하기 때문에 성립한다.)
\fi
\end{example}

@@

\ifen
Below are shown the first several iterations of Algorithm \ref{algorithmforlargeh}. The values of $f_j$, $t_j$, and their product are recorded only for the schools remaining in $\mathcal{C}$. $f * t$, where $(f * t)_j = f_j t_j$, denotes the entrywise product of $f$ and $t$. The school added at each iteration, underlined, is the one whose $f_j t_j$-value is greatest.
\else
아래에서 알고리즘 \ref{algorithmforlargeh}의 몇 반복단계가 나타난다. $f_j$, $t_j$, 그리고 그 곱의 값은 $\mathcal{C}$에 남아 있는 학교에 해당하는 값만 기록한다. $(f * t)_j = f_j t_j$로 정의된 $f * t$는 $f$와 $t$의 원소 당 곱을 의미한다. 각 반복단계에서 최적해에 추가하는 학교는 $f_j t_j$-값이 가장 높은 학교이며 이를 밑줄로 강조한다.
\fi
\newcommand{\Iteration}{\ifen Iteration~\else 반복단계~\fi}
\begin{align*}
\text{\Iteration 1:}
&&C &= \{1, 2, 3, 4, 5, 6, 7, 8\} \\
&&f &= \{0.39, 0.33, 0.24, 0.24, 0.05, 0.03, 0.1, 0.12\} \\
&&t &= \{200, 250, 300, 350, 400, 450, 500, 550\} \\
&&f * t &= \{78.0, 82.5, 72.0, \underline{84.0}, 20.0, 13.5, 50.0, 66.0\} 
~~\tag*{\(\implies \mathcal{X}_3 = \{4\} \)}\\
\text{\Iteration 2:}
&&C &= \{1, 2, 3, 5, 6, 7, 8\} \\
&&f &= \{0.39, 0.33, 0.24, 0.05, 0.03, 0.1, 0.12\} \\
&&t &= \{152, 190, 228, 316, 366, 416, 466\} \\
&&f * t &= \{59.28, \underline{62.7}, 54.72, 15.8, 10.98, 41.6, 55.92\} 
~~\tag*{\(\implies \mathcal{X}_3 = \{4, 2\} \)}\\
\text{\Iteration 3:}
&&C &= \{1, 3, 5, 6, 7, 8\} \\
&&f &= \{0.39, 0.24, 0.05, 0.03, 0.1, 0.12\} \\
&&t &= \{101.84, 165.3, 253.3, 303.3, 353.3, 403.3\} \\
&&f * t &= \{39.718, 39.672, 12.665, 9.099, 35.33, \underline{48.396}\} 
~~\tag*{\(\implies \mathcal{X}_3 = \{4, 2, 8\} \)}\\
&&&\cdots\\
\text{\Iteration 8:}
&&C &= \{6\}, f = \{0.03\}, t = \{177.622\}, f * t= \{\underline{5.329}\}
~~\tag*{\(\implies \mathcal{X}_3 = \{4, 2, 8, 1, 7, 3, 5, 6\} \)}
\end{align*}
\ifen 
The output of the algorithm is $\mathtt{X} = [4, 2, 8, 1, 7, 3, 5, 6]$, and the optimal $h$-portfolio consists of its first $h$ entries. The ``priority'' column of Table \ref{planetsdata} shows the inverse permutation of $\mathtt{X}$, which is the minimum value of $h$ for which the school is included in the optimal portfolio. Figure \ref{planetsplot} shows the value of the optimal portfolio as a function of $h$. The concave shape of the plot suggests the result of Theorem \ref{concavityinh}. 
\else
알고리즘의 출력은 $\mathtt{X} = [4, 2, 8, 1, 7, 3, 5, 6]$이며 최적 $h$-포트폴리오는 그의 첫 $h$개의 원소로 이루어진다. 표 \ref{planetsdata}에서 등장하는 ``지원 순위'' 자료는 $\mathtt{X}$의 역순열(inverse permutation)이며 이는 해당 학교가 최적 포트폴리오에 포함되는 최소한 $h$-값을 의미한다. 그림 \ref{planetsplot}은 최적 포트폴리오의 가치를 $h$의 함수로 나타낸다. 곡선의 오목성은 정리 \ref{concavityinh}의 결과를 시사한다.
\fi

\begin{table}[h!] \centering
\small
\begin{tabular}{r|lcccc}
\ifen\textbf{Index $j$} & \textbf{School $c_j$} & \textbf{Utility $t_j$} & \textbf{Admit prob. $f_j$} & \textbf{Priority} & \textbf{$v(\mathcal{X}_h)$} \\ \hline
\else 
\textbf{지표 $j$} & \textbf{학교 $c_j$} & \textbf{효용 $t_j$} & \textbf{합격 확률 $f_j$} & \textbf{지원 순위} & \textbf{$v(\mathcal{X}_h)$} \\ \hline  \fi
\\[-.75em]
1 & \ifen Mercury University   \else  수성대       \fi        & 200 & 0.39 & 4   & 230.0   \\
2 & \ifen Venus University     \else  금성대       \fi        & 250 & 0.33 & 2   & 146.7  \\
3 & \ifen Mars University      \else  화성대       \fi        & 300 & 0.24 & 6   & 281.5  \\
4 & \ifen Jupiter University   \else  목성대       \fi        & 350 & 0.24 & 1   & \phantom{0}84.0  \\
5 & \ifen Saturn University    \else  토성대       \fi        & 400 & 0.05 & 7   & 288.8  \\
6 & \ifen Uranus University    \else  천왕성대     \fi        & 450 & 0.03 & 8   & 294.1  \\
7 & \ifen Neptune University   \else  해왕성대     \fi        & 500 & 0.10 & 5   & 257.7  \\
8 & \ifen Pluto College        \else  명왕성대       \fi        & 550 & 0.12 & 3   & 195.1              
\end{tabular}
\caption{\label{planetsdata} \normalsize
\ifen College data and optimal application portfolios for a fictional market with $m=8$ schools. By the nestedness property (Theorem \ref{nestedapplication}), the optimal portfolio when the application limit is $h$ consists of the $h$ schools having priority $h$ or less.
\else
$m=8$개의 학교로 이루어진 가상 입학 시장의 대학교 자료와 최적 지원 포트폴리오. 포함 사슬 관계 성질(정리 \ref{nestedapplication})에 따라, 지원 제한이 $h$일 때 최적 포트폴리오는 지원 순위가 $h$ 이하인 $h$개의 학교로 구성된다.
\fi}
\end{table}

@@

\ifen \subsection{Summary of results} \else \subsection{결과 정리}\fi
\ifen
In our first experiment, we compare the performance of Algorithm \ref{algorithmforlargeh} for homogeneous-cost markets of various sizes when the set of candidate schools $\mathcal{C}$ is stored as a list and as a binary max heap ordered by the $f_j \bar t_j$-values. The results appear in Table \ref{experiment1results}. Our results indicate that the list implementation is faster. However, the ratio between the average times of the two implementations stays roughly constant, suggesting that a more effective heap implementation could be competitive in certain classes of problem instances. Overall, the rate of growth is quadratic in $m$, which accords with the $O(hm)$ time complexity result of Theorem \ref{validityofalmaalgorithm}.
\else
첫번째 실험에서, 동일한 지원 비용으로 정의된 크기가 다양한 시장에 대해 알고리즘 \ref{algorithmforlargeh}의 성능을 고려했다. 이를 $\mathcal{C}$를 목록 혹은 $f_j \bar t_j$-값에 따라 배열된 힙 구현으로 구성하는 경우로 나눴으며 실험 결과는 표 \ref{experiment1results}에서 등장한다. 실험 결과에 따라 목록 구현이 더 빠른 해법이었다. 그러나, 두개의 방법 사이에 계산 시간 비율은 거의 상수이므로 개선된 힙 해법이 어떤 문제 인스턴스에 대해 더 빠를 가능성이 있어 보인다. 전체적으로 계산 시간은 $m$의 제곱으로 늘아나며 이는 정리 \ref{validityofalmaalgorithm}에서 말한 $O(hm)$-시간과 동의한다.
\fi

@@

\begin{table}[h!] \centering
\small
\begin{tabular}{r|r@{~}r|r@{~}r}
\ifen 
 \textbf{\begin{tabular}[r]{@{}r@{}}Number of\\schools $m$\end{tabular}}& \multicolumn{2}{c|}{\textbf{\begin{tabular}[c]{@{}c@{}}Algorithm \ref{algorithmforlargeh}\\with list\end{tabular}}}  & \multicolumn{2}{c}{\textbf{\begin{tabular}[c]{@{}c@{}}Algorithm \ref{algorithmforlargeh}\\with heap\end{tabular}}}\\ \hline
 \else
 \textbf{\begin{tabular}[r]{@{}r@{}}학교의\\개수 $m$\end{tabular}}& \multicolumn{2}{c|}{\textbf{\begin{tabular}[c]{@{}c@{}}알고리즘 \ref{algorithmforlargeh}\\(목록 구현)\end{tabular}}}  & \multicolumn{2}{c}{\textbf{\begin{tabular}[c]{@{}c@{}}알고리즘 \ref{algorithmforlargeh}\\(힙 구현)\end{tabular}}}\\ \hline
 \fi
    16 &     0.00 &  (0.00) &      0.01 &    (0.00) \\
    64 &     0.01 &  (0.00) &      0.13 &    (0.03) \\
   256 &     0.14 &  (0.02) &      1.56 &    (0.57) \\
  1024 &     2.21 &  (0.35) &     41.65 &   (10.55) \\
  4096 &    35.36 &  (4.96) &   5080.63 & (6266.66) \\
 16384 &   552.45 & (79.57) &  16452.20 & (5525.29)       
\end{tabular}
\caption{\label{experiment1results} \normalsize
\ifen Time to compute an optimal portfolio for an admissions market with homogeneous application costs using Algorithm \ref{algorithmforlargeh} when $\mathcal{C}$ is stored as a list and as a heap. \lastptofcaption~In every case, $h = m/2$. 
\else 알고리즘 \ref{algorithmforlargeh}에서 $\mathcal{C}$를 목록 또는 힙 구현으로 저장했을 때, 
동일 지원 비용 입학 시장의 최적 지원 포트폴리오를 계산하는 시간. \lastptofcaption~모든 경우, $h = m/2$. \fi}
\end{table}

\begin{table}[h!] \centering
\small
\begin{tabular}{r|r@{~}r|r@{~}r|r@{~}r|r@{~}r}
\ifen
\textbf{\begin{tabular}[r]{@{}r@{}}Number of\\schools $m$\end{tabular}}&\multicolumn{2}{c|}{\textbf{\begin{tabular}[c]{@{}c@{}}Algorithm \ref{ellisbnb}:\\Branch \& bound\end{tabular}}}  & \multicolumn{2}{c|}{\textbf{\begin{tabular}[c]{@{}c@{}}Algorithm \ref{ellisDP1}:\\App. costs DP\end{tabular}}}  &\multicolumn{2}{c|}{\textbf{\begin{tabular}[c]{@{}c@{}}Algorithm \ref{ellisDP3}:\\FPTAS, $\varepsilon= 0.5$\end{tabular}}}  & \multicolumn{2}{c}{\textbf{\begin{tabular}[c]{@{}c@{}}Algorithm \ref{ellisDP3}:\\FPTAS, $\varepsilon= 0.05$\end{tabular}}}   \\ \hline
\else
\textbf{\begin{tabular}[r]{@{}r@{}}학교의\\개수 $m$\end{tabular}}&\multicolumn{2}{c|}{\textbf{\begin{tabular}[c]{@{}c@{}}알고리즘  \ref{ellisbnb}:\\분지한계법\end{tabular}}}  & \multicolumn{2}{c|}{\textbf{\begin{tabular}[c]{@{}c@{}}알고리즘 \ref{ellisDP1}: 지원\\비용 동적 계획\end{tabular}}}  &\multicolumn{2}{c|}{\textbf{\begin{tabular}[c]{@{}c@{}}알고리즘 \ref{ellisDP3}:\\FPTAS, $\varepsilon= 0.5$\end{tabular}}}  & \multicolumn{2}{c}{\textbf{\begin{tabular}[c]{@{}c@{}}알고리즘 \ref{ellisDP3}:\\FPTAS, $\varepsilon= 0.05$\end{tabular}}}   \\ \hline
\fi
   8 &          0.44 &       (0.42) &         0.06 &      (0.02) &                0.39 &             (0.16) &                 1.66 &              (0.64) \\
  16 &       3298.08 &    (5285.45) &         0.48 &      (0.16) &                2.64 &             (0.96) &                19.20 &              (7.05) \\
  32 &             — &          (—) &         2.30 &      (0.83) &               19.01 &             (9.18) &               184.00 &             (70.15) \\
  64 &             — &          (—) &         8.33 &      (3.52) &              101.05 &            (59.47) &              2089.30 &            (961.43) \\
 128 &             — &          (—) &        36.61 &     (15.36) &              481.61 &           (210.68) &              8626.29 &           (2615.38) \\
 256 &             — &          (—) &       205.57 &     (52.98) &             3106.71 &           (957.95) &             69291.93 &          (34881.04) \\
 512 &             — &          (—) &      1136.18 &    (396.24) &            16613.99 &          (6241.99) &            206020.31 &          (45217.42) 
\end{tabular}%
\caption{\label{experiment2results} \normalsize
\ifen Time to compute an optimal or $(1 - \varepsilon)$-optimal portfolio for an admissions market with heterogeneous application costs using the three algorithms developed in section \ref{hetappcosts}.
%branch-and-bound routine (Algorithm \ref{ellisbnb}), exact dynamic program (Algorithm \ref{ellisDP1}), and the fully polynomial-time approximation scheme (Algorithm \ref{ellisDP3}).
The branch-and-bound algorithm is impractical for large markets. \lastptofcaption
\else  %분지한계법 (알고리즘 \ref{ellisbnb}), 정확한 동적 계획 (알고리즘 \ref{ellisDP1}), 그리고 완전 다항 시간 근사 해법 (알고리즘 \ref{ellisDP3})을
 \ref{hetappcosts}절에서 도출한 3개의 알고리즘을 사용할 때, 다양한 지원 비용으로 갖춘 입학 시장의 최적 또는 $(1- \varepsilon)$-최적 포트폴리오를 계산하는 시간. 분지한계법은 큰 시장에서 비실용적이다. \lastptofcaption \fi}
\end{table}

@@

% Another ex of nestedness.
%Tibshirani, Robert. 1996. ``Regression Shrinkage and Selection via the Lasso.'' \emph{Journal of the Royal Statistical Society,. Series B (Methodological)} 58, no. 1: 267--88. \url{https://www.jstor.org/stable/2346178}.
